Dealing with Consumer Uncertainty: Online Product Reviews and What makes them helpful?

### 2022-06-03 Paper.Rmd
not much of a change

However, the increased rate of electronic commerce activity also created an abundance of product reviews on the internet. The vast amount of product reviews might increase the information overload on the customer [@sun2019; @fan2021]. Unfortunately, this information overload can make the search process even costlier because it is really time consuming to evaluate thousand of customer reviews. Additionally, not all reviews have the same informativeness level @pan2011. Therefore, answering the question of "what makes a helpful review?" is very important because reading more and more reviews can only increase the search cost. To make the understanding of a "helpful review" more clear we can define them as "*a peer-generated product evaluation that facilitates the consumer's purchase decision process*" @mudambi2010.

Since OCR don't share the same level of informativeness and usefulness @pan2011, most of the electronic retail websites implemented a very well known "helpfulness" feature to their customer review systems in order to help their customers navigate through thousand of reviews. On some websites, this feature is implemented in a way that helpful / unhelpful buttons are present and on some other websites, there is only a helpful button. In this paper, we acquired data from websites which support helpful / unhelpful system since it was found that helpfulness as a percentage (helpful votes over total votes) creates more powerful results than considering only helpful votes as a count variable @ahmad2015.

The research on perceived helpfulness is still growing. In Social and Behavioral Sciences, it is common to have conflicting papers and results in the literature @hunter1991. In this case, the study on perceived helpfulness is not an exception. Because of this reason, We think more empirical studies on perceived helpfulness are required. This paper aims to add one more perspective to growing literature of customer reviews and review helpfulness.

@@

Many independent variables and their relationship between perceived helpfulness was examined by researchers. Hong et al. (2017) @hong2017 groups these independent variables into two chunks. The first group is reviewer-related predictors. Variables within this group tries to understand the relationship between reviewer status and perceived helpfulness(reviewer expertise, number of past reviews etc.). [@sun2019; @ghose2011]. The second group tries to understand the review-related relationships such as review length, review extremity, discrete review emotion etc [@mudambi2010; @ghose2011; @ren2019; @eslami2018]. Ghose et al. (2011) @ghose2011 showed that review-related predictors have stronger prediction power than reviewer-related ones. The choice of the variables is of course heavily dependent on the data itself. In this paper, we only examined review-related predictors.

Review Length(Depth) could be considered as one of the most important independent variable explaining perceived helpfulness. It might be implemented in different ways but for the majority of the studies it is the word count in a given review. For most of the researchers, longer reviews contain more information about the product. As the potential buyer gets more information from a single review, he decreases his search costs with minimum effort [@mudambi2010; @hong2017; @liu2014; @wang2018; @korfiatis2012; @lee2016; @lee2014; @choi2020]. However, other group of researchers found out that there was a threshold on review length, meaning longer reviews might have useless information in them[@schindler2012; @huang2015]. Another group indicates the word count of the review shows diminishing returns to helpfulness, supporting the threshold idea [@baek2012; @kuan2015; @eslami2018].

@@

-   mention negative positive words here

@@

1.  Words in a review were tokenized.
2.  Tokenized words were matched with the lexicon.
3.  Matches were counted and divided by the total number of words with the respective review then multiplied by 100 in order to make regression results more interpretable.
4.  Logarithmic transformation was applied in order to scale the variable in a better way.

@@

-   method

>>>>

However, the increased rate of electronic commerce activity also created an abundance of product reviews on the internet. The vast amount of product reviews might increase the information overload on the customer [@sun2019; @fan2021]. Unfortunately, this information overload can make the search process even costlier because it is really time consuming to evaluate thousand of customer reviews. Additionally, not all reviews have the same informativeness level @pan2011. Therefore, answering the question of "what makes a helpful review?" is very important because reading more and more reviews can only increase the search cost. To make the understanding of a "helpful review" more clear it can defined as "*a peer-generated product evaluation that facilitates the consumer's purchase decision process*" @mudambi2010.

Since OCR don't share the same level of informativeness and usefulness @pan2011, most of the electronic retail websites implemented a very well known "helpfulness" feature to their customer review systems in order to help their customers navigate through thousand of reviews. On some websites, this feature is implemented in a way that helpful / unhelpful buttons are present and on some other websites, there is only a helpful button. In this paper, the data was acquired from websites which support helpful / unhelpful system since it was found that helpfulness as a percentage (helpful votes over total votes) creates more powerful results than considering only helpful votes as a count variable @ahmad2015.

The research on perceived helpfulness is still growing. In Social and Behavioral Sciences, it is common to have conflicting papers and results in the literature @hunter1991. In this case, the study on perceived helpfulness is not an exception. Because of this reason, more empirical studies on perceived helpfulness are required. This paper aims to add one more perspective to growing literature of customer reviews and review helpfulness.

@@

Many independent variables and their relationship between perceived helpfulness were examined by researchers. Hong et al. (2017) @hong2017 groups these independent variables into two chunks. The first group is reviewer-related predictors. Variables within this group tries to understand the relationship between reviewer status and perceived helpfulness(reviewer expertise, number of past reviews etc.). [@sun2019; @ghose2011]. The second group tries to understand the review-related relationships such as review length, review extremity, discrete review emotion etc [@mudambi2010; @ghose2011; @ren2019; @eslami2018]. Ghose et al. (2011) @ghose2011 showed that review-related predictors have stronger prediction power than reviewer-related ones. The choice of the variables is of course heavily dependent on the data itself. In this paper, only review-related predictors were examined.

Review Length (Depth) could be considered as one of the most important independent variable explaining perceived helpfulness. It might be implemented in different ways but for the majority of the studies it is the word count in a given review. For most of the researchers, longer reviews contain more information about the product. As the potential buyer gets more information from a single review, he decreases his search costs with minimum effort [@mudambi2010; @hong2017; @liu2014; @wang2018; @korfiatis2012; @lee2016; @lee2014; @choi2020]. However, other group of researchers found out that there was a threshold on review length, meaning longer reviews might have useless information in them[@schindler2012; @huang2015]. Another group indicates the word count of the review shows diminishing returns to helpfulness, supporting the threshold idea [@baek2012; @kuan2015; @eslami2018].

@@

The counts of negative or positive words out of total word count (the proportion of negative and positive words) were employed by a handful of studies [@baek2012; @kuan2015]. These metrics can measure the sentiment of the review itself. They are usually different than Review Extremity. In most cases Review Extremity and Review Sentiment (Valence) don't match @zhang2011. Both Baek et al. (2012) @baek2012 and Kuan et al. (2015) @kuan2015 discovered a positive relationship between the proportion of negative words and perceived helpfulness. The relationship between the proportion of positive words and perceived helpfulness was found to be negative @kuan2015.

@@

1.  Words in a review were tokenized.
2.  Tokenized words were matched with the words in the lexicon.
3.  Matches were counted and divided by the total number of words with the respective review then multiplied by 100 in order to make regression results more interpretable.
4.  Logarithmic transformation was applied in order to scale the variable in a better way.

@@

So far it should be understood that people try to cut down their losses. That is why negative cues draw more attention than positive ones. It is known that Review Rating is the satisfaction level of a customer towards a product. However, Review Rating itself isn't enough to convey the information about how a customer expresses her satisfaction / dissatisfaction towards a product. The way a customer expresses her opinion on a product might have an effect on the perceived helpfulness of a review. In this case

-   negativity bias/ negative info is more diagnostic than positive/ literature etc./ mention that review extremity and review sentiment are different things.

```{=html}
<!-- -->
```
-
